---
title: "Sunglasses project Study 4_analyses"
author: "Dallas Novakowski"
date: "28/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r required packages & data, warning=F,  message=F}
library(repmis)
library(ggpubr)
library(car)
library("dplyr")


source_data("https://github.com/DallasNovakowski/Shady_Eyes/blob/master/sunglasses_study4_clean2_11_27_2019.Rdata?raw=true")
```


```{r trasform variables to factors, include=FALSE}
data_reduced4$shade <- factor(data_reduced4$shade, 
                  levels = c(0, 1, 2),
                  labels = c("Clear", "Medium", "Dark"))
                  
str(data_reduced4$male_model)

data_reduced4$male_model <- factor(data_reduced4$male_model, 
                  levels = c(0, 1),
                  labels = c("Female Model", "Male Model"))
```

# Evaluations of Phoniness
## ANOVA
```{r ANOVA on phoniness}
res.aov.phony <- aov(phony ~ shade + male_model + shade:male_model, data = data_reduced4)
summary(res.aov.phony)

group_by(data_reduced4, male_model, shade) %>%
  summarise(
    count = n(),
    mean = mean(phony, na.rm = TRUE),
    sd = sd(phony, na.rm = TRUE)
  )
```

```{r ANOVA phoniness assumptions, include=FALSE}
TukeyHSD(res.aov.phony, which = "shade")

plot(res.aov.phony, 1)
leveneTest(phony ~ shade*male_model, data = data_reduced4)
plot(res.aov.phony, 2)
phony_residuals <- residuals(object = res.aov.phony)
# Run Shapiro-Wilk test
shapiro.test(x = phony_residuals )
```

```{r phony factorial boxplots, include=FALSE}
#p_phony_xgender <- ggboxplot(data_reduced4, x = "male_model", y = "phony",
 #         color = "shade", palette = "jco",
  #        add = "jitter")
#p_phony_xgender + stat_compare_means(aes(group = shade), label = "p.format")


# shade on x-ais, grouped by gender
#p_phony_xshade <- ggboxplot(data_reduced4, x = "shade", y = "phony",
 #         color = "male_model", palette = "jco",
  #        add = "jitter")
#p_phony_xshade + stat_compare_means(aes(group = male_model), label = "p.format")
```

## phoniness boxplots
```{r phony univariate boxplots, echo=FALSE}
compare_means(phony ~ shade,  data = data_reduced4)

shade_comparisons <- list( c("Clear", "Medium"), c("Clear", "Dark"), c("Medium", "Dark") )

p_phony_shade <- ggboxplot(data_reduced4, x = "shade", y = "phony",
          color = "shade", palette = "jco",
          add = "jitter") + 
  stat_compare_means(comparisons = shade_comparisons, label.y = c(2.8, 3.5, 4.5)) + # Add pairwise comparisons p-value
  # Add pairwise comparisons p-value
  stat_compare_means(label.y = 4.5) 
  
p_phony_shade

p_phony_gender <- ggboxplot(data_reduced4, x = "male_model", y = "phony",
          palette = "jco",
          add = "jitter") + 
  # Add pairwise comparisons p-value
  stat_compare_means(label.y = 3.2)


p_phony_gender
```
 
# Willingness to buy
## Anova on willingness to buy
```{r ANOVA on wtb, echo=FALSE}
res.aov.wtb <- aov(wtb ~ shade + male_model + shade:male_model, data = data_reduced4)
summary(res.aov.wtb)

group_by(data_reduced4, male_model, shade) %>%
  summarise(
    count = n(),
    mean = mean(wtb, na.rm = TRUE),
    sd = sd(wtb, na.rm = TRUE)
  )
```

## Boxplots on willingness to buy
```{r wtb boxplots, echo=FALSE}
p_wtb_shade <- ggboxplot(data_reduced4, x = "shade", y = "wtb",
          color = "shade", palette = "jco",
          add = "jitter") + 
  stat_compare_means(comparisons = shade_comparisons, label.y = c(8, 9, 10)) + # Add pairwise comparisons p-value
  # Add pairwise comparisons p-value
  stat_compare_means(label.y = 11) 
  
p_wtb_shade

p_wtb_gender <- ggboxplot(data_reduced4, x = "male_model", y = "wtb",
          palette = "jco",
          add = "jitter") + 
  # Add pairwise comparisons p-value
  stat_compare_means(label.y = 8)

p_wtb_gender
```

# Perceived perceived product value
## ANOVA on perceived product value
```{r ANOVA on value, echo=FALSE}
res.aov.value_assess <- aov(value_assess_num ~ shade + male_model + shade:male_model, data = data_reduced4)
summary(res.aov.value_assess)

group_by(data_reduced4, male_model, shade) %>%
  summarise(
    count = n(),
    mean = mean(value_assess_num, na.rm = TRUE),
    sd = sd(value_assess_num, na.rm = TRUE)
  )
```

## Boxplots on perceived product value
```{r boxplots on value, echo=FALSE}
p_value_shade <- ggboxplot(data_reduced4, x = "shade", y = "value_assess_num",
          color = "shade", palette = "jco",
          add = "jitter") + 
  stat_compare_means(comparisons = shade_comparisons, label.y = c(1700, 1900, 2150)) + # Add pairwise comparisons p-value
  # Add pairwise comparisons p-value
  stat_compare_means(label.y = 2300) 
  
p_value_shade

p_value_gender <- ggboxplot(data_reduced4, x = "male_model", y = "value_assess_num",
          palette = "jco",
          add = "jitter") + 
  # Add pairwise comparisons p-value
  stat_compare_means(label.y =1800) 

p_value_gender
```


# Likelihood to recommend
## ANOVA on likelihood to recommend
``` {r anova on recommend, echo=FALSE}
res.aov.recommend <- aov(recommend ~ shade + male_model + shade:male_model, data = data_reduced4)
summary(res.aov.recommend)

group_by(data_reduced4, male_model, shade) %>%
  summarise(
    count = n(),
    mean = mean(recommend, na.rm = TRUE),
    sd = sd(recommend, na.rm = TRUE)
  )
```


## Boxplots on likelihood to recommend
```{r boxplots on recommend, echo=FALSE}
p_recommend_shade <- ggboxplot(data_reduced4, x = "shade", y = "recommend",
          color = "shade", palette = "jco",
          add = "jitter") + 
  stat_compare_means(comparisons = shade_comparisons, label.y = c(8, 9, 10)) + # Add pairwise comparisons p-value
  # Add pairwise comparisons p-value
  stat_compare_means(label.y = 10) 
  
p_recommend_shade

p_recommend_gender <- ggboxplot(data_reduced4, x = "male_model", y = "recommend",
          palette = "jco",
          add = "jitter") + 
  # Add pairwise comparisons p-value
  stat_compare_means(label.y = 9)

p_recommend_gender
```


# Summary
The results indicate significant main effects of model gender and shade on perceived phoniness, with no interaction.

Neither shade nor model gender had significant effects on willingness to buy, perceived product value, nor likelihood to recommend the product 